Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-20 paper-2023-acsos-pulverization.tex
write the conclusion

openness

more platforms

global policies

>>>>

In this work we presented a practical \ac{dsl} and framework for the
runtime re-configuration of pulverised \ac{cps} applications.
%
The original idea of pulverisation was to define applications considering arbitrary networks of logical devices,
decompose (pulverise) these logical devices into small deployment units,
and then define their desired deployment at a later time.
%
Through the specialised \ac{dsl} introduced in this work
we have shown that this idea can be realised in practice.
%
Moreover, we extended the original idea of pulverisation with the possibility to specify runtime re-configuration policies,
which can be leveraged to achieve better trade-offs in terms of performance, cost, and resource usage.
%
We provide a real-world demonstrator for the technology,
and we show via simulation that the approach can be beneficial.

In the future,
we plan to extend the \ac{dsl} to support openness and collective reconfiguration policies.
%
The former will allow devices to join and leave the system at runtime,
while the latter will allow reconfigurations to be performed on the basis of a collective state of the system.
%
Concurrently,
we intend to add support for additional network protocols to be able to support a larger number of practical scenarios.
